Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-21 Docs/IJES/journal.tex
fix formulas

\vspace{-2 mm}
\begin{align}
\label{objective-function}
minimize\quad h_x 
\end{align}

@@

\vspace{-2 mm}
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|Ex| \leq S_0
\end{align}

\vspace{-2 mm}
\begin{align}
\label{hw-sw-partitioning2}
x \in \{0,1\}^n 
\end{align}

\vspace{2 mm}
\textcolor{blue}{Where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.

>>>>

\vspace{-2 mm}
\begin{align}
\label{objective-function}
minimize\quad h_x.
\end{align}

@@

\vspace{-2 mm}
\begin{align}
\label{hw-sw-partitioning}
s\left(1-x\right) + c|Ex| \leq S_0,
\end{align}

\vspace{-2 mm}
\begin{align}
\label{hw-sw-partitioning2}
x \in \{0,1\}^n, 
\end{align}

\vspace{2 mm}
\noindent \textcolor{blue}{where $h$, $s$ and $c$ are the vectors representing the cost functions, $E$ is the transposed incidence matrix of $G$ (indicating which edges cross the boundary between the contexts of hardware and software), $n$ is the number of nodes, and $x$ represents the decision variable (a binary vector indicating the partition: $1$ if the node is realized in hardware and $0$ if the node is realized in software)}. Concerning the complexity of this problem, \cite{Arato2003} demonstrate that it is NP-Hard, as defined in~\cite{Cormem}.
